---
title: "Test Dataset Creation For Corpora"
author: "Pier Lorenzo Paracchini"
date: "7 mai 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE, echo= T}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
Sys.setlocale(category = "LC_ALL",locale = "English_United States.1252")
source("./../scripts/corpora.R")
```

# Test Dataset from the Corpora (Twitter, News & Blogs)

Note! __`eval = F`__ in the `setup` code chunck!

Test dataset is created from each corpus wth random sampling approach, using a different seed from the one used to generate the training data. 

```{r loadingAndSamplingTheCorpora}
corpora.raw <- load_original_corpora()
corpora.sampled <- sample_corpora(corpora = corpora.raw, seed = 19411016, twitter.perc = 0.005, news.perc = 0.01, blogs.perc = 0.01)
```

# Cleaning the Sampled Corpora

The sampled corpora is going to be cleaned used the steps that have been previously used for the training data.

```{r cleanSampleCorpora}
# corpora.sampled <- list(twitterCorpus = c("Twitter Please RT it and http://test.com/pparacch/177065 u r c'mon doin' ma'am I'm doing it!👦",
#                                           "Twitter 12345       FUCK ass PIppero, I'm going to work a lot .... , _ test",
#                                           "ciao"),
#                          newsCorpus = c("News Please RT it and http://test.com/pparacch/177065 u r c'mon doin' ma'am I'm doing it!👦",
#                                         "News 12345       FUCK ass PIppero, I'm going to work a lot .... , _ test",
#                                         "ciao"),
#                          blogsCorpus = c("Blogs Please RT it and http://test.com/pparacch/177065 u r c'mon doin' ma'am I'm doing it!👦",
#                                          "Blogs 12345       FUCK ass PIppero, I'm going to work a lot .... , _ test",
#                                          "ciao"))

corpora.cleaned <- corpora_remove_short_entries(corpora = corpora.sampled, minNoOfChars = 40)
corpora.cleaned <- corpora_text_cleaning(corpora = corpora.cleaned)
corpora.transformed <- corpora_transform(corpora = corpora.cleaned)

test.twitters <- data.frame(entry = sapply(corpora.transformed$twitterCorpus,as.character))
test.news <- data.frame(entry = sapply(corpora.transformed$newsCorpus,as.character))
test.blogs <- data.frame(entry = sapply(corpora.transformed$blogsCorpus,as.character))

save(test.twitters, test.news, test.blogs, file = "./../data/processed/s02_04_corpora_testdataset.Rdata")
rm(list = ls())
load(file = "./../data/processed/s02_04_corpora_testdataset.Rdata")
```

Test dataset is going to be used for identify a set of sentences (realistic sentence)  and to create a set of sentences (not very realistic/ improbable). The latest set shoudl get the lower probability or higher perplexity.