---
title: "Models & Reduced Ngrams"
author: "Pier Lorenzo Paracchini"
date: "15 mai 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# WINDOWS LOCALE SETTING
Sys.setlocale(category = "LC_ALL",locale = "English_United States.1252")

require(knitr)

source("./../scripts/model_evaluation.R")
source("./../model/model_supportingFunctions.R")
source("./../model/model_stupidBackoff.R")
```

# Testing Sentences

```{r creatingTestDataSetOfSentences, collpase = T}
sentences

sentences_1
```

# Tri-gram model based on Stupid Backoff

Using all of the trigrams, bigrams and unigrams within all of the sample corpus to calculate the score for a specific sequence of words. In order to avoid the 0 score - especially when a term is not known, the unigram will return OTH probability (OTH has been introduced when reducing the list of UNIGRAMS to be used).


```{r loadTheNgramData, cache = T, collapse=T}
s.corpora.1g <- readRDS("./../model/model.1g.rds")
s.corpora.2g <- readRDS("./../model/model.2g.rds")

s.corpora.3g <- readRDS("./../model/model.3g.rds")
s.corpora.3g <- data.frame(terms = paste(s.corpora.3g$before.bigram, s.corpora.3g$next.word), total = s.corpora.3g$total, stringsAsFactors = F)
saveRDS(s.corpora.3g, file = "./../model/model.3g.withTrigrams.rds")

#Size of the object in memory
format(object.size(s.corpora.3g$terms), "auto")
format(object.size(s.corpora.3g$total), "auto")

format(object.size(s.corpora.2g$terms), "auto")
format(object.size(s.corpora.2g$total), "auto")

format(object.size(s.corpora.1g$terms), "auto")
format(object.size(s.corpora.1g$total), "auto")
```

```{r testStupidBackOff_3g_30_2g_75_1g_95_model1, collapse=T}
stupidBackoff.model.base.evaluation <- sapply(sentences, FUN = estimateSentenceProbabilities,
                                   t.terms = s.corpora.3g$terms, t.counters = s.corpora.3g$total,
                                   b.terms = s.corpora.2g$terms, s.corpora.2g$total,
                                   u.words = s.corpora.1g$terms, u.counters = s.corpora.1g$total)
colnames(stupidBackoff.model.base.evaluation) <- NULL
stupidBackoff.model.base.evaluation <- t(stupidBackoff.model.base.evaluation)
model1.perplexity <- calculatePerplexity(stupidBackoff.model.base.evaluation)
```

`r kable(stupidBackoff.model.base.evaluation, caption = "Tri-grams StupidBackoff")`

__Perplexity (log base2):__ `r model1.perplexity`

```{r testStupidBackOff_3g_30_2g_75_1g_95_model2, collapse=T}
stupidBackoff.model.base.evaluation2 <- sapply(sentences_1, FUN = estimateSentenceProbabilities,
                                   t.terms = s.corpora.3g$terms, t.counters = s.corpora.3g$total,
                                   b.terms = s.corpora.2g$terms, s.corpora.2g$total,
                                   u.words = s.corpora.1g$terms, u.counters = s.corpora.1g$total)
colnames(stupidBackoff.model.base.evaluation2) <- NULL
stupidBackoff.model.base.evaluation2 <- t(stupidBackoff.model.base.evaluation2)
model2.perplexity <- calculatePerplexity(stupidBackoff.model.base.evaluation2)
```

`r kable(stupidBackoff.model.base.evaluation2, caption = "Tri-grams StupidBackoff")`

__Perplexity (log base2):__ `r model2.perplexity`


