---
title: "Models & Reduced Ngrams: shiny App costraints"
author: "Pier Lorenzo Paracchini"
date: "22 mai 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# WINDOWS LOCALE SETTING
Sys.setlocale(category = "LC_ALL",locale = "English_United States.1252")
```

# Data Optimization for using Stupid Backoff Trigram model as App Engine

Using all of the trigrams, bigrams and unigrams within all of the sample corpus to calculate the score for a specific sequence of words. In order to avoid the 0 score - especially when a term is not known, the unigram will return OTH probability (OTH has been introduced when reducing the list of UNIGRAMS to be used).

## Trigrams

Required data structure:

* term
* next.word
* t.count
* b.count
* score (calculated using the count(trigram)/count(bigram))


```{r trigramsOptimization, collapse=T}
s.corpora.1g <- readRDS("./data/04_reducedTermFrequency/model.1g.rds")
s.corpora.2g <- readRDS("./data/04_reducedTermFrequency/model.2g.rds")


s.corpora.3g <- readRDS("./data/04_reducedTermFrequency/model.3g.rds")
s.corpora.3g$terms = paste(s.corpora.3g$before.bigram, s.corpora.3g$next.word)
names(s.corpora.3g) <- c("term", "next.word", "t.count", "trigram")

tmp <- merge(x = s.corpora.3g,  y = s.corpora.2g, by.x = "term", by.y = "terms", all.x = T)
tmp$scores <- tmp$t.count/ tmp$total

app.3g <- data.frame(term = tmp$term, next.word = tmp$next.word, t.count = tmp$t.count, b.count = tmp$total, score = tmp$scores)
app.3g <- app.3g[order(app.3g$score, decreasing = T),]

idx <- which(app.3g$term == "are u")
app.3g <- app.3g[-idx,]

idx <- which(app.3g$term == "the s")
app.3g <- app.3g[-idx,]

idx <- which(nchar(as.character(app.3g$next.word)) == 1 & app.3g$next.word != "a" & app.3g$next.word != "i")
unique(app.3g$next.word[idx])
app.3g <- app.3g[-idx,]

app.3g$term <- as.character(app.3g$term)
app.3g$next.word <- as.character(app.3g$next.word)
#Size of the object in memory
format(object.size(app.3g), "auto")

saveRDS(app.3g, file = "./data/05_modelsForApp/app.3g.rds")
rm(list = ls())
```

## Bigrams

Required data structure:

* term
* next.word
* b.count
* u.count
* score (calculated using the count(bigram)/count(unigram))


```{r bigramsOptimization, collapse=T}
s.corpora.1g <- readRDS("./data/04_reducedTermFrequency/model.1g.rds")
s.corpora.2g <- readRDS("./data/04_reducedTermFrequency/model.2g.rds")

s.corpora.2g$term1 <- sapply(X = s.corpora.2g$terms, FUN = function(x){unlist(strsplit(x, " "))[1]})
s.corpora.2g$term2 <- sapply(X = s.corpora.2g$terms, FUN = function(x){unlist(strsplit(x, " "))[2]})
names(s.corpora.2g) <- c("bigram", "b.count", "word1", "word2")

tmp <- merge(x = s.corpora.2g,  y = s.corpora.1g, by.x = "word1", by.y = "terms", all.x = T)
tmp$score <- 0.4 * (tmp$b.count/ tmp$total)

app.2g <- data.frame(term = tmp$word1, next.word = tmp$word2, b.count = tmp$b.count, u.count = tmp$total, score = tmp$score)
app.2g <- app.2g[order(app.2g$score, decreasing = T),]


idx <- which(nchar(as.character(app.2g$term)) == 1 & app.2g$term != "a" & app.2g$term != "i")
##Removing single chars
unique(app.2g$term[idx])
app.2g <- app.2g[-idx,]

idx <- which(nchar(as.character(app.2g$next.word)) == 1 & app.2g$next.word != "a" & app.2g$next.word != "i")
##Removing single chars
unique(app.2g$next.word[idx])
app.2g <- app.2g[-idx,]

str(app.2g)
app.2g$term <- as.character(app.2g$term)
app.2g$next.word <- as.character(app.2g$next.word)
str(app.2g)

#Size of the object in memory
format(object.size(app.2g), "auto")

saveRDS(app.2g, file = "./data/05_modelsForApp/app.2g.rds")
rm(list = ls())
```

## Unigrams

Required data structure:

* term
* count
* score (calculated using count(term)/N)


```{r unigramsOptimization, collapse=T}
s.corpora.1g <- readRDS("./data/04_reducedTermFrequency/model.1g.rds")
N <- sum(s.corpora.1g$total)
s.corpora.1g$score <- 0.4 * 0.4 * (s.corpora.1g$total/ N)

app.1g <- data.frame(term = s.corpora.1g$terms, count = s.corpora.1g$total, score = s.corpora.1g$score)

app.1g$term <- as.character(app.1g$term)

#Size of the object in memory
format(object.size(app.1g), "auto")

saveRDS(app.1g, file = "./data/05_modelsForApp/app.1g.rds")
```
